Analysing Constraint Grammars with a SAT-solver

### 2016-03-07 paper/lrec/eval_futurework.tex
small cleanup

\subsection{Performance} 
The running time of the grammars goes from seconds to hours. 
As can be seen from the times, increasing the number of readings
matters more than increasing the number of rules.
In addition, the ambiguity class constraints take a long time.

@@

Another benefit of this solution is the addition of lemmas and word
forms, as well as regular expressions: currently, if we want to add
one more lemma for a verb, we need to create as many new variables as
there are distinct verb forms---easily hundreds for languages with
rich morphology.

>>>>

\subsection{Performance} 
The running time of the grammars goes from seconds to hours. 
As can be seen from the times, increasing the number of readings
matters more than increasing the number of rules.
In addition, the ambiguity class constraints increase the time.

@@
